%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%                               80 COLONNES                                %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Publications et Réalisations}
\label{AnxPubReal}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{-0.5cm}


\section*{Publications}
\label{SecAnxPubSci}


\subsection*{Conférences~/ \lang{workshops}}

\begin{itemize}

\item Moutie Chehaider, Kévin Roussel, Ye-Qiong Song.
<<~Interopérabilité des réseaux de capteurs hétérogènes dans
un appartement intelligent~>>
\textit{9èmes journées francophones Mobilité et Ubiquité}, UbiMob 2013.
Nancy, France. Juin 2013.

\item Kévin Roussel.
<<~Implementing a real-time MAC protocol under RIOT OS : running on
Zolertia Z1 motes~>>
In \textit{Workshop Internet of Things / Equipex FIT IoT-LAB},
INRIA Grenoble Rhone-Alpes, Montbonnot, France. Novembre 2014.
(présentation sans actes.)

\item Kévin Roussel, Ye-Qiong Song, Olivier Zendra.
<<~RIOT OS Paves the Way for Implementation of High-performance
MAC Protocols~>>
In \textit{Proceedings of the 4th International Conference
on Sensor Networks}, SensorNets 2015, pages 5--14.
ESEO, Angers, France. Février 2015.

\item Kévin Roussel, Ye-Qiong Song, Olivier Zendra.
<<~ Using Cooja for WSN Simulations: Some New Uses and Limits ~>>.
In \textit{Proceedings of the 2016 International Conference on Embedded
Wireless Systems and Networks}~--- EWSN~'16~; \lang{workshop NextMote},
pages 319--324.
\lang{Technische Universit\"at}, Graz, Autriche. Février 2016.

\end{itemize}


\subsection*{Rapports de recherche INRIA (HAL)}

\begin{itemize}

\item Kévin Roussel, Ye-Qiong Song.
<<~A critical analysis of Contiki's network stack for integrating
new MAC protocols~>>. 13 pages. Décembre 2013.\\
Rapport de recherche INRIA \no~8776 \textit{(CRI-Nancy Grand Est)}.\\
ID hal-01202542.

\item Kévin Roussel, Ye-Qiong Song, Olivier Zendra.
<<~Practical Lessons Learned through Implementation and Performance
Evaluation of Two MAC/RDC Protocols on WSN OS~>> 25 pages. Mars 2015.\\
Rapport de recherche INRIA \no~8777 \textit{(CRI-Nancy Grand Est)}.\\
ID hal-01202664.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Réalisations techniques (\lang{``Pull Requests''} sur GitHub)}
\label{SecAnxRealTech}


\subsection*{Pour Contiki OS}

Ces deux contributions ont été refusées (mais réutilisées en partie et
indirectement pour une amélioration ultérieure de l'API radio de Contiki~:
PR \#617 de Niklas Finne et~al, intégrée au code de Contiki OS en juin 2014).


\begin{itemize}

\item Kévin Roussel, George Oikonomou, Mariano Alvira, David Kopf,
      Valentin Sawadski, Joakim Eriksson, Peter A. Bigot, Adam Dunkels.
PR \#192~: <<~Extended radio drivers API~>>.
(2013--2014).

\item Kévin Roussel, Mariano Alvira, Joakim Eriksson, George Oikonomou,
      Oliver Schmidt, Adam Dunkels, Nicolas Tsiftes.
PR \#519~: <<~Radio api extension~>>.
(2014).

\end{itemize}


\subsection*{Pour RIOT OS}

Toutes les contributions citées ci-dessous dans la présente section
ont été acceptées et ont été intégrées (\lang{``merged PRs''})
à la branche principale du code de RIOT OS.


\begin{itemize}

\item Kévin Roussel, Ludwig Knüpfer, Oliver Hahm, Thomas Eichinger.
PR \#408~: <<~Simplify msp430 headers~>>
(2013).

\item Kévin Roussel, Oliver Hahm, Ludwig Knüpfer.
PR \#459~: <<~Msp430 lpm freq~>>
(2013--2014).

\item Kévin Roussel, Oliver Hahm, Kaspar Schleiser, Ludwig Knüpfer,
      Christian Mehlis, René Kijewski.
PR \#685~: <<~Panic~>>
(2014).\\
\emph{Best PR award of the month (Février 2014).}

\item Kévin Roussel, René Kijewski, Oliver Hahm, Ludwig Knüpfer,
      Christian Mehlis.
PR \#687~: <<~Add a \texttt{reboot()} function to \texttt{kernel.h}
              definitions~>>
(2014).

\item Kévin Roussel, René Kijewski, Kaspar Schleiser.
PR \#689~: <<~Portable definition of function attributes~>>
(2014).

\item Kévin Roussel, René Kijewski, Oliver Hahm, Ludwig Knüpfer.
PR \#724~: <<~Reboot~>>
(2014).

\item Kévin Roussel, René Kijewski, Oliver Hahm.
PR \#881~: <<~Ensure that stack pointer is correcty aligned during
              thread creation on MSP430~>>
(2014).

\item Kévin Roussel, Oliver Hahm, Thomas Eichinger.
PR \#882~: <<~CC2420 radio tranceiver's driver fixes~>>
(2014).

\item Kévin Roussel, Oliver Hahm, Ludwig Knüpfer, Christian Mehlis,
      Thomas Eichinger, Hauke Petersen.
PR \#893~: <<~Zolertia Z1 port for RIOT OS~>>
(2014).

\item Kévin Roussel, Ludwig Knüpfer, Thomas Eichinger, Oliver Hahm,
      René Kijewski.
PR \#915~: <<~Add a standard way to query CCA status on CC2420 transceiver~>>
(2014).

\item Kévin Roussel, Oliver Hahm, Ludwig Knüpfer, Thomas Eichinger,
      Martine Lenders, Hauke Petersen.
PR \#925~: <<~Proposal for common 802.15.4 radio driver API definition~>>
(2014).

\item Kévin Roussel, Oliver Hahm.
PR \#954~: <<~Fix for CC2420 radio driver for TelosB~>>
(2014).

\item Kévin Roussel, Oliver Hahm, Ludwig Knüpfer.
PR \#957~: <<~Handle race conditions preventing MSP430 timers to be set
              correctly~>>
(2014).

\item Kévin Roussel, René Kijewski, Kaspar Schleiser, Ludwig Knüpfer,
      Oliver Hahm, Christian Mehlis.
PR \#970~: <<~core: Add the ability to send a message to the current
              thread's message queue~>>
(2014).

\item Kévin Roussel, Ludwig Knüpfer, René Kijewski, Oliver Hahm,
      Christian Mehlis, Kaspar Schleiser.
PR \#1002~: <<~Enhance implementation of \texttt{hwtimer\_ spin()}~>>
(2014).

\item Kévin Roussel, Oliver Hahm, Ludwig Knüpfer.
PR \#1113~: <<~Use Timer B on MSP430 architecture~>>
(2014).

\item Kévin Roussel, Oliver Hahm.
PR \#1211~: <<~Completing low-level radio driver definition~>>
(2014).

\item Kévin Roussel, Oliver Hahm, Thomas Eichinger, Christian Mehlis.
PR \#1223~: <<~Modify \& extend CC2420 driver to comply with API described
               in \texttt{radio\_ driver.h}~>>
(2014).

\item Kévin Roussel, Oliver Hahm.
PR \#1239~: <<~Add a missing constant in \texttt{'radio\_ tx\_status\_t'}
               enum~>>
(2014).

\item Kévin Roussel, René Kijewski, Hauke Petersen, Ludwig Knüpfer,
      Christian Mehlis, Oliver Hahm.
PR \#1380~: <<~Reset ARM Cortex-M3 MCUs before flashing~>>
(2014).

\item Kévin Roussel, Ludwig Knüpfer, Oliver Hahm.
PR \#1383~: <<~Fix a design error in \texttt{cc2420\_do\_send()} function~>>
(2014).

\item Kévin Roussel, Ludwig Knüpfer, Oliver Hahm.
PR \#1385~: <<~Fix a nasty race condition in CCA determination on CC2420~>>
(2014).

\item Kévin Roussel, Oliver Hahm.
PR \#1388~: <<~boards/z1: fix \texttt{cc2420\_txrx} function in CC2420
               driver HAL~>>
(2014).

\item Kévin Roussel, Ludwig Knüpfer, Hauke Petersen, Kaspar Schleiser.
PR \#1617~: <<~Ensure \texttt{hwtimer\_spin()} won't wait for
               an unreachable stop counter value~>>
(2014).

\item Kévin Roussel, Ludwig Knüpfer, Oliver Hahm, Hinnerk van Bruinehsen.
PR \#1618~: <<~Fix \texttt{thread\_yield()} on MSP430 platforms~>>
(2014).

\item Kévin Roussel, Ludwig Knüpfer, Oliver Hahm, Hinnerk van Bruinehsen,
      Martine Lenders.
PR \#1619~: <<~Only use 16 significative bits for MSP430 \texttt{hwtimer}s~>>
(2014).

\item Kévin Roussel, Oliver Hahm, Ludwig Knüpfer.
PR \#2214~: <<~Msp430 misc interrupt-related fixes~>>
(2014).

\item Kévin Roussel, Jonas Remmert, Oliver Hahm
PR \#4138~: <<~Add a \texttt{netopt} for getting and setting CCA threshold~>>
(2015).

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%            FIN DE L'ANNEXE "PUBLICATIONS ET RÉALISATIONS"             %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




